---
title: Unstable Equilibria
description: !!Change this!!
author: Braden
date: '2020-03-12'
slug: unstable-equilibria
categories:
  - Business Strategy
tags:
  - coronavirus
  - covid-19
draft: no
images:
  -
---

```{r}
library(tidyverse)
library(bayestestR)
```

```{r}
# create distributions
x <- rnorm_perfect(n = 100, mean = 0, sd = 1)
z <- rnorm_perfect(n = 100, mean = 2, sd = 1)

# add x distribution to plot
p <- x %>% 
  density() %>%
  as.data.frame() %>% 
  ggplot(aes(x=x, y=y)) +
  geom_line()

# add z distribution to plot
p <- p + geom_line(data = as.data.frame(density(z)), aes(x=x, y=y))
```

Over the last few weeks, the Coronavirus, more properly known as COVID-19, has been on my mind more than anything else. I follow several tech people on Twitter who were early voices sounding the alarm on COVID-19 - primarily [Balaji Srinivasan](https://twitter.com/balajis) and [Scott Gottlieb](https://twitter.com/ScottGottliebMD). Normally, I'm fairly conservative and skeptical of warnings like these. Fortunately, however, Balaji, Scott, and others convinced me through their in-depth and informative tweets that COVID-19 was going to be a serious crisis in just a matter of a few weeks. My wife and I took a trip to Costco to stock up on non-perishables like peanut butter and toilet paper (the essentials) and were able to avoid the rush that has been increasing as the public has become more fearful and hoarding.

I have struggled to decide when I should sound the alarm myself and begin warning family, friends, and everyone else around me in my professional life. I expected four possible outcomes:

```{r}
empty_theme <- theme(                              
  plot.background = element_blank(), 
  panel.grid.major = element_blank(), 
  panel.grid.minor = element_blank(), 
  panel.border = element_blank(), 
  panel.background = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.text.y = element_text(angle = 90)
)

plot <- ggplot(NULL, aes()) +
  # fix the scale so it's always a square
  coord_fixed() +
  # set the scale to one greater than 0-10 in each direction
  # this gives us some breating room and space to add some arrows
  scale_x_continuous(expand = c(0, 0), limits = c(-1, 11),
                     breaks = c(2,8), labels=c("2" = "", "8" = "")) +
  scale_y_continuous(expand = c(0, 0), limits = c(-1,11),
                     breaks = c(2,8), labels=c("2" = "", "8" = "")) +
  # apply the empty theme
  empty_theme +
  # labels
  labs(title = "Potential Outcomes",
       x = "",
       y = "") +
  # create the quadrants
  geom_segment(aes(x = 10, y = 0, xend = 10, yend = 10)) +
  geom_segment(aes(x = 0, y = 0, xend = 0, yend = 10)) +
  geom_segment(aes(x = 0, y = 0, xend = 10, yend = 0)) +
  geom_segment(aes(x = 0, y = 5, xend = 10, yend = 5)) +
  geom_segment(aes(x = 5, y = 0, xend = 5, yend = 10)) +
  geom_segment(aes(x = 0, y = 10, xend = 10, yend = 10)) +
  # quadrant labels
  annotate("text", x = -.5, y = 2.5, angle = 90, label = "Don't warn") +
  annotate("text", x = -.5, y = 7.5, angle = 90, label = "Warn") +
  annotate("text", x = 2.5, y = 10.5, label = "Crisis is avoided") +
  annotate("text", x = 7.5, y = 10.5, label = "Crisis occurs") +
  # quadrant titles
  annotate("text", x = 2.5, y = 2.5, color = "#AA0000", label = "Dull") +
  annotate("text", x = 2.5, y = 7.5, color = "#AA0000", label = "Gullible") +
  annotate("text", x = 7.5, y = 2.5, color = "#AA0000", label = "Smart") +
  annotate("text", x = 7.5, y = 7.5, color = "#AA0000", label = "Selfish")

plot
```








