---
title: Reflecting on my 2019 goals
author: Braden
date: '2020-01-03'
slug: reflecting-on-my-2019-goals
categories:
  - Reflection
tags:
  - goals
  - failure
  - metrics
  
draft: no

twitter:
  card: "summary"
  site: "@braden_live"
  title: Reflecting on my 2019 goals
  description: At the beginning of 2019, I set a number of goals for myself. Here's how I did.
  image: 'https://www.bradenlive.com/posts/'
---

I've never been one for New Year's Resolutions. I always thought the entire process was artificial -- why make resolutions based upon an arbitrary number from the calendar?

I held this view up until last year, when my wife convinced me to come along with her for her "end-of-year reflection"...a few hours at our local coffee shop ([Colectivo](https://colectivocoffee.com/cafes/evanston) in Evanston, if you're wondering). We spent the time thinking about everything that happened in the past year (2018) including a Navy deployment for me, medical issues for her, and starting school at Kellogg. Each of us also thought about how we wanted to shape the coming year, and wrote down our goals. It was a useful exercise -- we repeated it this year.

Looking back at what I wrote a year ago has been illuminating. Over the course of 2019, the goals I set were never completely out of mind, but I also never deliberately looked back at my journal to see precisely what I had written or how I had progressed in completing the goals, and my impression from memory was that I was nowhere close to completing any of them. Today, however, I was surprised to find that I actually completed a several of them, and made significant progress on even more.

I encourage everyone to complete an end-of-year reflection, in whatever format works best. 

***

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(kableExtra)

type <- c('daily', 'daily', 'habit', 'habit', 'habit', 'seasonal', 'seasonal', 'year-long', 'year-long', 'year-long', 'year-long', 'year-long')
status <- factor(c('complete', 'incomplete', 'push', 'push', 'incomplete', 'complete', 'complete', 'complete', 'complete', 'push', 'push', 'incomplete'), levels = c('complete', 'push', 'incomplete'))

results <- data.frame(type, status)

# this works ------------------------------------
# ggplot(results, aes(x = status)) +
#   geom_dotplot(aes(fill = status), binwidth = .2) +
#   facet_grid(vars(type)) +
#   theme_minimal() +
#   theme(panel.background = element_rect(fill = NA, color = "black"),
#         panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank(),
#         panel.spacing = unit(0, "lines"),
#         axis.title.y = element_blank(),
#         axis.ticks.y = element_blank(),
#         axis.text.y = element_blank(),
#         legend.position = "none",
#         strip.text.y = element_text(angle = 360)) +
#   scale_fill_manual(values=c("#66a182", "#8d96a3", "#d1495b"))
# ------------------------------------------------

rows <- 2
cols <- 2

results %>%
  arrange(status, type) %>%
  group_by(status, type) %>%
  mutate(num = row_number(),
         x_pos = (num - 1) %/% rows,
         y_pos = rows - (num - 1) %% rows - 1) %>%

  ggplot(aes(x = x_pos, y = y_pos, fill = status)) +
  geom_tile(color = "black", width = .8, height = .8) +
  coord_equal(xlim = c(0, cols) - 0.5,
              ylim = c(0, rows) - 0.5) +
  facet_grid(vars(type), vars(status)) +
  theme_minimal() +
  theme(panel.background = element_rect(fill = NA, color = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.spacing = unit(0, "lines"),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        legend.position = "none",
        strip.text.y = element_text(angle = 360)) +
  scale_fill_manual(values=c("#66a182", "#8d96a3", "#d1495b"))
```

I divided 12 goals for the year into four categories based on how often I would have to think about them:

* **Daily:** goals where I would need to complete a task every single day
* **Habit:** goals where I would need to complete a task a few times every week
* **Seasonal:** goals that were related to a specific time of the year
* **Year-long:** long-term goals that might require sporadic effort throughout the year

```{r, echo=FALSE, message=FALSE, warning=FALSE}
results_table <- results %>%
  mutate(num = row_number())

emojis <- c(':thumbsup:', ':no_entry_sign:', ':white_circle:', ':white_circle:', ':no_entry_sign:', ':thumbsup:', ':thumbsup:', ':thumbsup:', ':thumbsup:', ':white_circle:', ':white_circle:', ':no_entry_sign:')

comments <- c(
  '**Better daily quiet time.** I wanted to have a more consistent and meaningful daily morning time reading Scripture. I set a plan to read the Old Testament once and New Testament twice over the course of the year. Although I missed about five days, I kept up and finished the plan on schedule.',
  '**Daily meditation.** My plan was to spend some time each day meditating in order to calm my mind from the fast past of business school. I ended up meditating for about five minutes immediately after my quiet time, but this habit ended by March.',
  '**Play guitar more.** In 2018, my time playing live music decreased after our move away from Virginia and the start of business school. I wanted to spend at least an hour a week practicing the guitar and learning songs. My goal was to learn one new song every month by heart. After three songs halfway memorized, this habit fell by the wayside in March as well.',
  "**Read more books.** I was hoping to be more intentional with how I spent my time as well as get to the mounting list of books I wanted to read - the goal was to read one book per month. Although I definitely read more, I didn't do a good job keeping track of my progress.",
  "**Get more fit.** I wanted to break my all time personal records (PRs) in bench press and deadlift (255 and 405 lbs, respectively). I went to the campus gym four days a week at 5:30am, but only managed to break my bench press PR (barely; I hit 260) due to several minor back injuries I sustained while deadlifting. I also performed poorly on the Navy's physical fitness test.",
  "**Go on spring break.** After being scared away from heading to Cancun due to the spectre of [dead seaweed](https://www.independent.co.uk/news/world/americas/rotting-seaweed-beaches-sargassum-mexico-carribbean-cancun-playa-del-carmen-tulum-a8978756.html) on the beach, we spent a week in Austin, Texas instead and loved it.",
  "**Go turkey and deer/bird hunting.** I spent an entire spring weekend hunting turkey with my brother-in-law on public land in southeastern Wisconsin, but we were unable to close the deal. In the fall, the two of us went pheasant hunting with our dogs and successfully bagged a few birds.",
  "**Save up for a house downpayment.** This was an exercise in futility. We don't plan to buy a house until after leaving the Navy a few years from now, and the fact that we're living on the edge of our budget with our current situation in Evanston meant we deprioritized this goal.",
  "**Create something.** I created an app called [BidVis](https://www.bradenlive.com/posts/bidvis/) using R. I also created this website. Finally, I came up with an idea to host a [military veterans panel](https://www.kellogg.northwestern.edu/executive-education/take-action/spark.aspx) for Kellogg Executive MBA students, which ended up being a great success.",
  "**Learn some business skills.** In combination with coursework at Kellogg and my work as a product manager intern at [Narrative Science](www.narrativescience.com), I learned to code in R and SQL, use Jira, and generally work in an Agile softward development environment.",
  "**Make friends at church.** My dual goals here were to join a small group and get involved in Sunday services (most likely playing the drums) at our church, [Renewal](http://www.renewalchicago.com/). We were able to do the first but not the second.",
  "**Get a tattoo.** I wanted to find an artist in Chicago to get a tattoo I've been considering for the last few years."
)








results_table <- cbind(results_table, emojis, comments) %>%
  select(num, everything(), -status)
kable(results_table)
```








